\documentclass[twoside]{article}%{combine}
%\usepackage{url}
\usepackage{../../tex/html}
\usepackage{epstopdf}
\usepackage{amsfonts,amsmath,color,amsthm,amssymb, enumerate, bbm, subfig}
\usepackage{graphicx}
%\usepackage[DIV=14,BCOR=2mm,headinclude=true,footinclude=false]{typearea}
%\usepackage[font=small,labelfont=bf]{caption}
\usepackage{hyperref}
\usepackage{tikz, etoolbox}

\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
%\usepackage[margin=1in]{geometry}
\input{../../tex/115}
\raggedbottom

\begin{document}

\prelab{6}{ The Transportation Problem}

\noindent

Objectives:

\begin{itemize}
\item   Introduce students to the transportation problem
\item   Give an application of the
transportation problem of the ``caterer's problem''
\end{itemize}

\noindent Key Ideas:
\begin{itemize}
\item   supply point and supply constraint
\item   demand point and demand constraint
\item   balanced transportation problem
\item   bipartite graph
\item   integrality properties
\item sensitivity analysis
\end{itemize}
\textbf{Reading Assignment:}
\begin{itemize}
\item
Read the first part of Handout 7 on the transportation problem (first 4 pages)\end{itemize}

\textbf{Brief description:}
In this lab, we will
\begin{enumerate}
\item Learn how to formulate a somewhat unexpected problem as a transportation problem
\item Continue to develop our facility in using Jupyter notebooks to solve optimization problems
\end{enumerate}

\smallskip
\noindent
Read and understand the problem, and think about how you would model it as a mathematical optimization problem (i.e., what is a feasible solution of the problem? What is the objective function? How can you express the objective functions and constraints every feasible solution must satisfy mathematically?). 


\smallskip
\noindent
\textbf{The Caterer's Problem} (From [Winston]) The Carter Caterer Company must have the following number of clean napkins available at the
beginning of each of the next four days: day 1, 15; day 2, 12; day
3, 18; day 4, 6. After being used, a napkin can be cleaned by one
of two methods: fast service or slow service. Fast service costs
10 cents per napkin, and a napkin cleaned via fast service is
available for use the day after it is last used. Slow service
costs 6 cents per napkin, and these napkins can be reused two days
after they are last used. New napkins can be purchased for a cost
of 20 cents per napkin. The catering company currently has no
napkins, whatsoever. We wish to meet the demand for the next four
days as cheaply as possible.

\begin{enumerate}
\item Give one feasible solution to the problem that uses all three options of obtaining clean
napkins - buying them new, cleaning them fast, or cleaning them slowly. Compute the 
objective function value for this solution.
\item Give a lower bound on the cost of {\it any} feasible solution.
\end{enumerate}
\end{document}
